---
title: 'Final Project: Is there a correlation between the popularity of manga and
  the ranking of their anime adaptations?'
author: "Sijie Wu"
date: "Aug 7, 2024"
output:
  html_document:
    df_print: paged
---

## Research Question and Dataset Introduction

The research question driving this analysis is: **"Is there a correlation between the popularity of manga and the ranking of their anime adaptations?"** To explore this, we utilized two comprehensive datasets sourced from Kaggle. The first dataset, Top Anime Ranked, is derived from MyAnimeList.net, a prominent platform for anime enthusiasts. This dataset encompasses a wide range of information, including unique identifiers (UID), titles, rankings, stream types, episodes, start and end dates, member counts, and user scores. It offers a detailed view of anime popularity, duration, and user ratings, making it a valuable resource for statistical analysis, machine learning applications, and trend exploration in anime viewership.

The second dataset, Best-Selling Manga, lists the most successful Japanese manga series based on the number of collected tankōbon volumes sold. This dataset includes manga series with at least 20 million copies in circulation, providing a reliable measure of their popularity. The data is organized by the highest circulation estimates recorded from credible sources, ensuring accurate representation of manga sales. By analyzing these datasets, we aim to uncover patterns and correlations between the success of manga and the performance of their corresponding anime adaptations, providing insights into the factors that contribute to the popularity of these media forms.

## Data Processing 

#### Data Intake 

```{r}
library(readr)

# Import the Top Anime Ranked dataset
Anime_rank <- read_csv("/Users/vivienwu/Downloads/Anime_rank.csv")

# Import the Best-Selling Manga dataset
best_selling_manga <- read_csv("/Users/vivienwu/Downloads/best-selling-manga.csv")

# Print the first few rows of each dataset to confirm successful import
head(Anime_rank)
head(best_selling_manga)
```


#### Data Wrangling 

The data wrangling process involved several key steps to prepare the datasets for analysis and visualization.
```{r}
# Load packages
library(dplyr)
library(tidyr)
library(readr)
library(stringr)
library(ggplot2)

# View the structure of the datasets
str(Anime_rank)
str(best_selling_manga)

# Clean the Top Anime Ranked dataset
top_anime_cleaned <- Anime_rank %>%
  select(Title, Rank, Score, Members) %>% # Select relevant columns
  filter(!is.na(Title) & !is.na(Rank)) %>% # Remove rows with missing values in key columns
  mutate(Title = str_trim(Title))          # Trim whitespace from titles

# Clean the Best-Selling Manga dataset
best_selling_manga_cleaned <- best_selling_manga %>%
  select(`Manga series`, `Approximate sales in million(s)`) %>% # Select relevant columns
  filter(!is.na(`Manga series`) & !is.na(`Approximate sales in million(s)`)) %>% # Remove rows with missing values in key columns
  mutate(`Manga series` = str_trim(`Manga series`))                             
# Trim whitespace from manga series names

# Merge the two datasets
merged_data <- top_anime_cleaned %>%
  inner_join(best_selling_manga_cleaned, by = c("Title" = "Manga series"))

# Print the first few rows of the merged dataset
head(merged_data)

# Wrangled Datasets
top_50_anime_by_score <- top_anime_cleaned %>%
  arrange(desc(Score)) %>%
  top_n(50, Score)

# Top 50 Manga by Sales
top_50_manga_by_sales <- best_selling_manga_cleaned %>%
  arrange(desc(`Approximate sales in million(s)`)) %>%
  top_n(50, `Approximate sales in million(s)`)

# Print the first few rows of the additional wrangled datasets
head(top_50_anime_by_score)
head(top_50_manga_by_sales)
```
The cleaned and merged datasets allowed for effective visualization and analysis to explore the relationship between the popularity of manga and the ranking of their anime adaptations.

```{r}
# Boxplot for anime scores
ggplot(top_anime_cleaned, aes(x = "", y = Score)) +
  geom_boxplot() +
  labs(title = "Boxplot of Anime Scores",
       y = "Score")

# Boxplot for manga sales
ggplot(best_selling_manga_cleaned, aes(x = "", y = `Approximate sales in million(s)`)) +
  geom_boxplot() +
  labs(title = "Boxplot of Manga Sales",
       y = "Manga Sales (in millions)")

# Boxplot for number of members
ggplot(top_anime_cleaned, aes(x = "", y = Members)) +
  geom_boxplot() +
  labs(title = "Boxplot of Number of Members",
       y = "Number of Members")

# Identify outliers in anime scores
anime_score_outliers <- top_anime_cleaned %>%
  filter(Score < quantile(Score, 0.25) - 1.5 * IQR(Score) | Score > quantile(Score, 0.75) + 1.5 * IQR(Score))

# Identify outliers in manga sales
manga_sales_outliers <- best_selling_manga_cleaned %>%
  filter(`Approximate sales in million(s)` < quantile(`Approximate sales in million(s)`, 0.25) - 1.5 * IQR(`Approximate sales in million(s)`) | 
         `Approximate sales in million(s)` > quantile(`Approximate sales in million(s)`, 0.75) + 1.5 * IQR(`Approximate sales in million(s)`))

# Identify outliers in number of members
members_outliers <- top_anime_cleaned %>%
  filter(Members < quantile(Members, 0.25) - 1.5 * IQR(Members) | Members > quantile(Members, 0.75) + 1.5 * IQR(Members))

# Print outliers
anime_score_outliers
manga_sales_outliers
members_outliers
```
The data wrangling process involved several key steps to prepare and clean the datasets for analysis. We began by loading the necessary packages (dplyr, tidyr, readr, and stringr) for data manipulation and importing. The structure of the datasets Anime_rank and best_selling_manga was inspected to understand their data types and arrangement. For the Top Anime Ranked dataset, we selected relevant columns (Title, Rank, Score, Members), removed rows with missing values in key columns, and trimmed whitespace from the Title column. Similarly, for the Best-Selling Manga dataset, we selected relevant columns (Manga series, Approximate sales in million(s)), removed rows with missing values, and trimmed whitespace from the Manga series column. The cleaned datasets were then merged using an inner join on the Title and Manga series columns, combining the datasets based on matching titles. Additionally, we created two wrangled datasets: the top 50 anime by score and the top 50 manga by sales, by arranging the data in descending order of scores and sales, respectively, and selecting the top entries.

Following the data wrangling, we conducted an outlier analysis on key variables—anime scores, manga sales, and the number of members. Using boxplots, we identified outliers that represented data points significantly deviating from the rest of the dataset. Outliers in anime scores indicated variability in audience reception, with some anime receiving exceptionally high or low ratings. For manga sales, high outliers reflected the exceptional popularity of certain series, which could skew the analysis due to their significant influence. Outliers in the number of members highlighted anime with substantial fan bases, potentially affecting the correlation analysis. By accounting for these outliers, we ensured a more accurate understanding of the relationship between manga popularity and anime rankings, providing a robust foundation for our analysis.

## Data Visualization

```{r}
library(ggplot2)

# Create a scatter plot with a regression line
plot1 <- ggplot(merged_data, aes(x = Score, y = `Approximate sales in million(s)`, size = Members, color = Rank)) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm", se = FALSE, color = "blue", linetype = "dashed") +
  scale_size_continuous(range = c(1, 10), name = "Members") +
  scale_color_gradient(low = "yellow", high = "red", name = "Rank") +
  labs(title = "Relationship between Anime Score, Members, and Manga Sales",
       x = "Anime Score",
       y = "Manga Sales (in millions)") +
  theme_minimal() +
  theme(legend.position = "bottom")

# Print the plot
print(plot1)
```
This bar plot visualizes the relationship between the popularity of the top 20 manga (measured by approximate sales) and the ranking of their anime adaptations. This visualization helps in understanding the overall relationship between anime scores, manga sales, and the number of members. The trend line provides a visual cue for any existing correlation.

- X-axis (Anime Title): Represents the titles of the top 20 anime, ordered by their rank.
- Y-axis (Manga Sales): Represents the approximate sales of the manga series in millions.
- Bar Color (Anime Score): Represents the score of the anime, with a gradient from yellow (lower scores) to blue (higher scores).


```{r}
# Select the top 20 manga by sales
top_20_manga <- merged_data %>%
  arrange(desc(`Approximate sales in million(s)`)) %>%
  head(20)

# Create a bar plot to show the relationship between manga sales and anime ranking
plot2 <- ggplot(top_20_manga, aes(x = reorder(Title, -Rank), y = `Approximate sales in million(s)`, fill = Score)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  scale_fill_gradient(low = "yellow", high = "blue", name = "Anime Score") +
  labs(title = "Top 20 Manga Sales vs. Anime Ranking",
       x = "Anime Title",
       y = "Manga Sales (in millions)") +
  theme_minimal() +
  theme(legend.position = "bottom",
        axis.text.y = element_text(size = 10))

# Print the plot
print(plot2)
```
This bar plot visualizes the relationship between the popularity of the top 20 manga (measured by approximate sales) and the ranking of their anime adaptations. By focusing on the top 20 manga, this plot highlights specific cases where high manga sales correlate with high anime rankings, making it easier to identify patterns and outliers.

- X-axis (Anime Title): Represents the titles of the top 20 anime, ordered by their rank.
- Y-axis (Manga Sales): Represents the approximate sales of the manga series in millions.
- Bar Color (Anime Score): Represents the score of the anime, with a gradient from yellow (lower scores) to blue (higher scores).

## Conclusion

Our analysis sought to answer the research question: **"Is there a correlation between the popularity of manga and the ranking of their anime adaptations?"** Using comprehensive datasets from Kaggle, we examined the top-ranked anime and best-selling manga series, focusing on key variables such as anime scores, member counts, and manga sales.

The scatter plot visualizing the relationship between anime scores, manga sales, and member counts suggested a positive correlation. Higher manga sales generally corresponded to higher anime scores, and popular anime (with more members) often had higher sales figures. For instance, in the first ggplot graph, anime titles with high member counts and high scores, such as "One Piece," demonstrated significant manga sales, reinforcing the observed trend.

Additionally, the bar plot focusing on the top 20 manga by sales and their corresponding anime rankings provided a more nuanced view, indicating that while several top-selling manga had high-ranking anime adaptations, this trend was not uniform. From the second ggplot graph, we can see that the best-selling manga "One Piece" is also among the top 3 in anime rankings, illustrating a case where high manga sales coincide with a high-ranking anime adaptation. However, this trend was not consistent across all titles. Some high-selling manga had anime adaptations that did not perform as well in rankings.

From our initial intuition and the visualizations, we observe a trend where popular manga tend to have successful anime adaptations. However, the correlation is not absolute; high manga sales do not always guarantee a top-ranked anime adaptation. Factors such as production quality, fidelity to the source material, and audience reception significantly influence the success of an anime adaptation.

In conclusion, while there is some correlation between manga popularity and anime rankings, it is not a definitive predictor. The success of an anime adaptation is multifaceted, and manga popularity is just one of many contributing factors. Our findings highlight the complexity of the relationship between manga sales and anime success, suggesting that future research could delve deeper into other influential factors to provide a more comprehensive understanding.